\begin{abstract}
Layer skipping makes Transformer inference cheaper by deleting entire residual
blocks, and the operator it uses to do so is crude: it assumes the missing residual
update is exactly zero. That update is in fact partly predictable from the updates
that precede it. We introduce \textbf{\mname (Depth-wise AutoRegressive update
prediction)}, which replaces a skipped block with a closed-form autoregressive
forecast of its residual update, fitted per channel on unlabeled text with no
gradient training, at $O(Td)$ inference cost. \mname recovers a real and consistent
fraction of the \emph{likelihood} that skipping destroys --- \phm{10.3}\% of the
language-modelling damage at the deployable operating point of Qwen2.5-1.5B, and
more when layers are chosen to maximise it. Getting even this required discarding
the obvious version of the idea: a single global coefficient per layer fails, and
at some layers is worse than dropping the update outright; only a $d$-dimensional
coefficient vector works. But the recovery does not reach the model's
\emph{behaviour}. \mname's benefit to behaviour is real, but it appears only where plain skipping has
already destroyed the model: selecting layers to maximise recovery buys \phm{132}
additional correct answers out of \phm{900} on Qwen2.5-1.5B --- at a
language-modelling loss of \phm{5.99} against a dense \phm{2.33}, a model nobody
would deploy. At the operating point one would actually deploy, the effect on
accuracy is undetectable at our sample sizes: every delta, in either direction,
falls within one binomial standard error (\phm{$-6$} to $+\phm{5}$ answers), and
several tasks are exactly tied. We claim neither improvement nor harm there; we
claim that a large and consistent likelihood recovery buys neither. The same
dissociation appears
three times over: held-out predictability is uncorrelated with the damage
prediction repairs (Spearman \phm{$-0.015$}), an energy-weighted fit criterion
selects a ridge that leaves development loss at \phm{11.01} against a dense
\phm{2.73}, and likelihood recovery does not transfer to accuracy. Predictability,
energy-weighted metrics, and language-modelling loss recovery all systematically
overestimate functional repair.
\end{abstract}
