\section{Experimental Details and Additional Results}
\label{sec:app-experiments}

\subsection{Implementation and correctness checks}
\label{sec:app-correctness}

\mname is implemented as a wrapper around the decoder stack that intercepts the
residual update of each block. Before running any experiment we verified the
wrapper with six checks, all of which pass on Qwen2.5-0.5B (24 blocks, 22
eligible). The dense wrapper reproduces the unmodified model's logits
\textbf{bit-exactly} (maximum absolute logit difference $\phm{0.0}$), as do the
$\aal_\ell = \bm{0}$ reduction to Plain Skip (checked at layers \phm{5}, \phm{9} and
\phm{13}) and a hand-written single-layer skip (layer \phm{9}). Residual updates are
captured at the block boundary of \cref{eq:residual} to a maximum absolute error of
$\phm{3.8 \times 10^{-6}}$ against a hidden-state scale of $\phm{1.7 \times 10^{3}}$.
Scrambling the padded token slots moves neither the fitted accumulators nor the
held-out NLL ($\phm{0.0}$ change, \phm{192} real tokens counted), confirming that
padding is excluded from \cref{eq:fit}. The selected layer set is non-adjacent by
construction (minimum gap \phm{2}, first and last blocks excluded).

\subsection{Calibration and evaluation protocol}
\label{sec:app-protocol}

Coefficients are fitted on unlabeled WikiText-103 text \citep{merity2017pointer},
and $P_\ell$ is scored on a disjoint held-out split of the same size. The 0.5B
analysis uses \phm{16} calibration and 16 held-out sequences of length \phm{512},
and reports NLL on held-out WikiText-103; it runs in FP32 on an NVIDIA TITAN X
(Pascal) GPU. The 1.5B and \topscale runs use \phm{32} sequences of length
\phm{1024}, report NLL on the WikiText-2 test split, and run in BF16 on a single
NVIDIA RTX 3090 GPU. Statistics are accumulated in FP64 (\cref{eq:fit}) so that no
hidden states need to be stored. Task evaluation uses \phm{300} examples per task
with fixed example IDs and seed 42 throughout. No configuration uses
FlashAttention, so we use the reference attention implementation everywhere.
Absolute latencies are specific to this hardware, even though the relative
comparison between methods is not.

\subsection{Latency measurement}
\label{sec:app-latency}

We report \emph{prefill} latency only: a forward pass with
\texttt{use\_cache=False}, batch size \phm{8}, at sequence lengths 512 and 2048,
with \phm{10} warm-up iterations followed by \phm{30} measured iterations, and
\texttt{torch.cuda.synchronize()} around each timed region. We report the median
and interquartile range over synthetic inputs, on an NVIDIA RTX 3090 in BF16 with eager
attention, using the \Cref{tab:main} $k=4$ layer set, for both Qwen2.5-1.5B and
Qwen2.5-7B. On 7B at sequence length 512 the \mname-over-plain-skip overhead is
\phm{4.9}\,ms against interquartile ranges of \phm{1.19} and \phm{0.57}\,ms, so it is
resolvable; at 2048 the overhead is \phm{1.0}\,ms against interquartile ranges of
\phm{4.08} and \phm{4.16}\,ms, so at that length it is \emph{not} distinguishable from
measurement noise and we do not claim it is. Either way the overhead is well under one
percent, and the block-compute saving that motivates skipping is preserved. We make no
claim about end-to-end generation latency, which depends on decode-time behaviour we do
not measure here.

\subsection{Two taps buy nothing}
\label{sec:app-ar2}

We also evaluated a two-tap variant, $\widehat{\dd}_\ell = \alpha_\ell \dd_{\ell-1}
+ \beta_\ell \dd_{\ell-2}$, fitting $(\alpha_\ell, \beta_\ell)$ through a
$2\times2$ ridge system. Averaged over the eligible layers of Qwen2.5-0.5B it
improves single-layer recovery over the one-tap scalar by \phm{$+0.0009$} --- that
is, not at all. The information a second tap adds is negligible next to the
information a second \emph{channel} adds, which is the point of \cref{eq:diag}: the
useful axis of capacity here is across the hidden width, not back along depth. We
therefore report the one-tap predictor throughout and do not pursue longer windows.

\subsection{Depth is anti-correlated before it is autoregressive}
\label{sec:app-anticorr}

The momentum the
method assumes is not a general property of depth. Through the middle of
Qwen2.5-0.5B every fitted scalar coefficient is negative (layers 4--16, \phm{13} of
\phm{13}), and this is not an artifact of summarizing many channels with one number:
\phm{88}\% of the individual per-channel coefficients in that region are also
negative, with a median of \phm{$-0.19$}. Successive blocks there partially
\emph{undo} one another. Positive depth-wise momentum appears only in the last
quarter of the stack, and it is there --- together with the earliest layers --- that
the recoverable damage is concentrated.

\subsection{The ridge coefficient}
\label{sec:app-ridge}

\Cref{eq:fit} carries a ridge term $\epsilon$. We swept it over
$\{0, 10^{-2}, 10^{-1}, 1, 10\}$ and selected $\epsilon = \phm{0.01}$ by mean
single-layer NLL recovery on the development split; every number reported in the
paper is measured on the test split. Two observations are worth recording. First,
the ridge is a \emph{stability} guard, not a source of gains: across the tested
range it moves mean recovery by a few percent, and we make no claim that tuning it
matters. Second, it does not rescue layer 2, whose recovery stays deeply negative
at every strength tested (\phm{$-3.68$} at $\epsilon=0.01$, still \phm{$-2.42$} at
$\epsilon=10$); the pathology there lives in \emph{high}-energy channels, which a
ridge scaled to the layer's own energy cannot suppress. Layer 2 is never selected
by the recovery-based rule, so this does not affect any reported result --- but it
is a second instance of the paper's central theme, and we would rather report it
than let it go unmentioned.

\subsection{Predictability across depth}
\input{figures/fig1a_appendix}

The depth profile behind \Cref{fig:momentum} is shown in \Cref{fig:momentum-profile}.

\subsection{Full downstream results}
\label{sec:app-downstream}

\input{tables/main_table}

The per-task numbers behind \Cref{fig:dissociation} are given in \Cref{tab:main}.

\subsection{Accuracy deltas, sampling noise, and ratio inflation}
\label{sec:app-noise}

Recovered-gap \emph{fractions} on accuracy divide by a Dense-minus-Plain-Skip denominator
only tens of graded answers wide, and are correspondingly unstable. We therefore tested
every \mname-versus-Plain-Skip accuracy comparison against the standard error of a
difference of two proportions, and report absolute counts in the body. Of the \phm{16}
comparisons, \phm{14} are not significant at the two-sided $95\%$ level. A $1$-SE band is
not a significance test: a delta at $1.0$--$1.2$ SE has $p \approx 0.25$ and establishes
nothing.

Only \phm{2} comparisons are significant, and both survive Bonferroni correction over the
family of \phm{16} tests actually performed ($\alpha/m = \phm{0.003125}$, $|z| \ge
\phm{2.96}$): recovery-maximising selection on Qwen2.5-1.5B at $k=2$
($+\phm{132}$ answers, $z=\phm{6.45}$) and $k=4$ ($+\phm{90}$, $z=\phm{4.37}$). Both are
earned on models plain skipping has already destroyed. Correction matters here rather
than being ceremonial: an uncorrected $95\%$ threshold over \phm{16} tests would expect
about \phm{0.8} false positives by chance, so the uncorrected borderline case
(0.5B, recovery-top, $k=2$, $z=\phm{1.95}$) cannot be claimed.

We apply the test symmetrically. A delta inside the noise band is discounted whichever way
it points, so we neither credit \mname with the $+18.5\%$ that five answers produce at
$k=2$ on 1.5B, nor charge it with the $-6\%$ that four answers produce at $k=4$.

\subsection{Layer selection}
\label{sec:app-selection}

The three selection rules of \Cref{tab:selection} are: (i) \emph{predictability},
ranking layers by held-out $P_\ell$ (\cref{eq:pscore}), which requires only a
forward pass of the dense model and no skipping; (ii) \emph{lowest single-layer
damage}, ranking by the NLL increase caused by skipping each layer individually on
the development set; and (iii) \emph{measured recovery}, ranking by the fraction of
that damage the predictor repairs. Rules (ii) and (iii) require one forward pass
per candidate layer and are correspondingly more expensive than (i); only (i) is
free. That (i) is also the rule that fails is the practical sting of
\Cref{sec:experiments}. All rules enforce the same non-adjacency constraint, and
all predictors are compared at the identical layer set a rule produces.
